Top Text

### 2022-11-27 Paper.tex
the methods section's first iteration

\documentclass{report}

@@

@@

>>>>

\documentclass[]{report}
\renewcommand\thesection{\arabic{section}}%for page numbering in arabics
\usepackage{graphicx,tabularx}%for figures and tables
\usepackage[utf8]{inputenc} %allows special characters such as ä, ö, ỳ
\usepackage[english]{babel}  %set the language to English
\usepackage[margin=1.5in]{geometry} %change page margins 
\usepackage{sectsty}%section headers
\allsectionsfont{\sffamily\large}
\subsectionfont{\sffamily\normalsize}
\linespread{1.2}% line distance
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{caption}%use for captions on tables
%use this exact command. The style and bibliographystyle has to be authoryear (Havard). The sorting is nyt: name, year, title so that the bibliography is sorted alphabetically. firstinits=true shortens the names: Albert Einstein -> A. Einstein
\usepackage[backend=bibtex,style=authoryear,bibstyle=authoryear,sorting=nyt,firstinits=true]{biblatex}
\setlength\parindent{0pt}%include this so that your paragraphs don't indent automatically
\addbibresource{report.bib} %this attaches your bib-file, your bibliography (must be in the same folder)
\usepackage[compact]{titlesec}%include title formatting package

% Title Page
\title{Top Text}
\author{Tom Jacobs and James Boogaard}
\date{December 15th 2022 \\Module: SEAR \\Venlo, Limburg, Netherlands}

@@

	\maketitle

	\begin{abstract}
		This is the abstract.

		\pagenumbering{roman}

	\end{abstract}

	\tableofcontents
	\setcounter{page}{3}
	\listoffigures %UNCOMMENT IF YOU HAVE FIGURES
	%\listoftables %UNCOMMENT IF YOU HAVE TABLES
	\pagebreak

	\pagenumbering{arabic}

	\section{Introduction}
	During the year there has been a massive increase in the popularity of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image, which has led to many being made which on the one hand has given artist (a person that uses a text-to-image generator to create an image with text) many more options but has also made the landscape difficult to navigate. This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy so we can help give some perspective on which text-to-image generator is best for them.

	Research paper was released on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations. We wanted to see which one out of the four we chose was the best for the artist according to specific criteria.

	Our goal during the course of this reaserch paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation.

	The best text-to-image generator out of the four we chose will be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tume their result. Given enough time this will yield a more accurate result.

	\section{Methods}

	Our goal during the course of this research paper is to find out what the best text to image generator is, out of the four we chose, for artists who are experienced as well as artists who are not experienced in AI art generation.

	A secondary research question that we take a look at in this paper is to find out the strengths of the different ai text to image generation techniques used in the applications we have chosen.

	This paper is used as an attempt to prove that stable diffusion is the best application out of the four, we chose. Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications. The intervening variable in this case would be experience using these applications.

	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (30 minutes ) and after each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application. With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate. this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result. Once the data is gathered, we can create a graph to compare the applications more easily. The people that carried out this experiment also consisted of one novice and one experienced individual. This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs. In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.

	\section{Results}
	\newpage	
	\section{Discussion}

@@

\printbibliography[title=References]
